Better fusion for filters

### 2014-04-08 2014betterfusionforfilters/section/01-Introduction.tex
fix some citations

% NOTE: This set of bullets needs to fit on the first page, without spilling to the second.
\begin{itemize}
\item   
We use existing integer linear programming clustering formulations such as Megiddo\cite{megiddo1998optimal} and Darte\cite{darte2002contraction},
and modify them to express constraints on fusing loops of different sizes if they can be fused into generator loops of the same size.
\TODO{ref}
% We present an algorithm to cluster the operators of a data flow graph into sub-graphs that can be fused into individual imperative loops.
% We express the constraints on fusion as an integer linear program, and use an off-the-shelf solver to compute a valid clustering. \TODO{ref}

@@

The reduction of the clustering problem to integer linear programming was previously described by\cite{megiddo1998optimal}, though they do not consider filtering operations.

>>>>

% NOTE: This set of bullets needs to fit on the first page, without spilling to the second.
\begin{itemize}
\item   
We use existing integer linear programming clustering formulations such as Megiddo~\cite{megiddo1998optimal} and Darte~\cite{darte2002contraction},
and modify them to express constraints on fusing loops of different sizes if they can be fused into generator loops of the same size.
\TODO{ref}
% We present an algorithm to cluster the operators of a data flow graph into sub-graphs that can be fused into individual imperative loops.
% We express the constraints on fusion as an integer linear program, and use an off-the-shelf solver to compute a valid clustering. \TODO{ref}

@@

The reduction of the clustering problem to integer linear programming was previously described by~\cite{megiddo1998optimal}, though they do not consider filtering operations.
